Exploring Real Data: A look at AirBnB

### 2017-06-06 ArticleDraft.Rmd
Test Commit

### Exploration #8: 
Can you use the data to predict which neighborhood a rental is in based on other characteristics in the data?  Pick three or four neighborhoods which contain "many" rentals and keep only data from these neighborhoods.  Can you build a model (maybe hierarchical clustering, k-nearest neighbors, support vector classifiers, or something else) which can predict which neighborhood you're in, based on certain *important* variables? Which variables do you think you should use?  Do you think using `latitude` and/or `longitude` is like cheating?    How well does your model work?

@@

clusters<-na.omit(clusters)
km<-kmeans(cbind(clusters[,7:8]),5)
clusters<-clusters %>% mutate(Predict = km$cluster)

>>>>

### Exploration #8: 
Can you use the data to predict which neighborhood a rental is in based on other characteristics in the data?  Pick three or four neighborhoods which contain "many" rentals and keep only data from these neighborhoods.  Can you build a model (maybe hierarchical clustering, k-means, or something else) which can predict which neighborhood you're in, based on certain *important* variables? Which variables do you think you should use?  Do you think using `latitude` and/or `longitude` is like cheating?    How well does your model work?

@@

clusters<-na.omit(clusters)
km<-kmeans(cbind(clusters[,1:8]),5)
clusters<-clusters %>% mutate(Predict = km$cluster)
